---
title: "311 Exploratory Analysis"
author: "Michael Spencer, Andrew (Foster) Docherty, Jorge Nam Song, Lauren Feitzinger, Andrea Banuet"
date: "11/21/2019"
output: pdf_document
params:
  city: "SFO"
  write: "no"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
# Pathways
project_dir <- here::here()
data_city <- params$city
data_name <- paste0(data_city, "_data_census")
```

```{r, include=FALSE}
# Parameters
write_my_files <- params$write

race_colors <- 
  c(
    "White" = "darkblue", 
    "Hispanic" = "orange", 
    "African American" = "maroon", 
    "Asian" = "darkgreen"
  )
```

```{r, include=FALSE}
# Sourcing and Libraries
if (!require(sf)) install.packages("sf")
library(sf)

if (!require(tidyverse)) install.packages("tidyverse")
library(tidyverse)

if (!require(lubridate)) install.packages("lubridate")
library(lubridate)

if (!require(googlesheets4)) install.packages("googlesheets4")
library(googlesheets4)

if (!require(ggmap)) install.packages("ggmap")
library(ggmap)

if (!require(patchwork)) install.packages("patchwork")
library(patchwork)

# Source prep and cleaning files to load data
source(paste0(project_dir, "/scripts/311/final_clean.R"))

# Source file to write out summarized geojson file
if (write_my_files == "yes") {
	source(paste0(project_dir, "/scripts/311/shp_to_geojson.R"))
}

# Source support functions
source(paste0(project_dir, "/analysis/support_functions.R"))
```

## Checks
```{r, echo=FALSE, warning=FALSE}
# Check for uncategorized service requests and notify user
data_temp <- 
	data_calls %>% 
	filter(is.na(topic)) %>% 
	distinct(srvc_nm)

if (nrow(data_temp) > 0) {
	print(paste0(
		"There are currently ", 
		nrow(data_temp), 
		" uncategorized services in ", 
		data_city, 
		". See them below:"))
	
	for (i in data_temp) {
		print(i)
	}
} else {
	print("All services in the data have been classified!")
}
```

Potential duplicates. These are only adressed if it is believed they would present a significant issue in analysis.
```{r, echo=FALSE, warning=FALSE}
# Check for apparent duplicates and address if there is a problem
data_calls %>% 
	group_by(address, req_dt, updt_dt, topic) %>% 
	count(sort = TRUE, name = "n") %>% 
	filter(n > 1) %>% 
	ungroup() %>% 
	select(-address) %>% 
	head(100) %>% 
	knitr::kable()
```

\newpage
## Analysis

### Base Benchmark Analysis (Non-Geographic)

##### What is the distribution of call by topic?
```{r, echo=FALSE, warning=FALSE}
data_calls %>%
  count(topic, sort = TRUE) %>%
  mutate(prop_total = (n / sum(n)) %>% round(digits = 3)) %>%
  knitr::kable()

data_calls %>%
  count(topic, sort = TRUE) %>%
  mutate(
    prop = n / sum(n, na.rm = TRUE),
    topic = topic %>% fct_inorder() %>% fct_rev()
  ) %>%
  head(10) %>%
  ggplot(aes(x = topic, y = prop)) +
  geom_point() +
  coord_flip() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    title = "Most Frequent Request Topics",
    x = "Request Topic",
    y = "Proportion of Total Requests"
  )
```

##### Within the top five topics, what are the most frequent services requested?
```{r, include=FALSE}
data_temp <-
  data_calls %>%
  group_by(topic, srvc_nm) %>%
  summarize(total_service = n()) %>%
  mutate(
    total_topic = sum(total_service, na.rm = TRUE),
    service_prop_topic = (total_service / total_topic) %>% round(digits = 3)
  ) %>%
  ungroup() %>%
  mutate(topic_prop_all = total_topic / sum(total_service, na.rm = TRUE) %>% round(digits = 3)) %>%
  arrange(desc(total_topic), desc(total_service))

data_temp
```

```{r, echo=FALSE, warning=FALSE}
list_topics <- 
	data_temp %>%
  distinct(topic) %>%
  pull(topic)

plot_top_services <- function(tp) {
  data_temp %>%
    filter(topic == tp) %>%
    head(3) %>%
    mutate(srvc_nm = srvc_nm %>% fct_inorder() %>% fct_rev()) %>%
    ggplot(aes(x = srvc_nm, y = service_prop_topic)) +
    geom_point() +
    coord_flip() +
    scale_y_continuous(labels = scales::percent_format()) +
    labs(
      title = paste0("Frequently Requested Services:\n", tp %>% str_to_title()),
      x = "Requested Service",
      y = paste0("Proportion of Total Requests in Topic")
    )
}

map(head(list_topics), plot_top_services)
```

##### What is the proportion of requests that may be adversarial by topic?
```{r, echo=FALSE, warning=FALSE}
# Excludes "maybe" adversarial in calculations.

data_calls %>%
  group_by(topic) %>%
  summarise(
    tot_adversarial = sum(adv == "yes", na.rm = TRUE),
    tot_not_adversarial = sum(adv == "no", na.rm = TRUE)
  ) %>%
  mutate(
    prop_adversarial =
      tot_adversarial / (tot_adversarial + tot_not_adversarial),
    prop_not_adversarial =
    	tot_not_adversarial / (tot_adversarial + tot_not_adversarial)
  ) %>%
	arrange(desc(prop_adversarial)) %>% 
  knitr::kable()
```

##### What is the proportion of requests that may involve illegal acitivity by topic?
```{r, echo=FALSE, warning=FALSE}
# Excludes "maybe" illegal in calculations.

data_calls %>%
  group_by(topic) %>%
  summarise(
    tot_illegal = sum(illegal == "yes", na.rm = TRUE),
    tot_not_illegal = sum(illegal == "no", na.rm = TRUE)
  ) %>%
  mutate(
    prop_illegal =
      tot_illegal / (tot_illegal + tot_not_illegal),
    prop_not_illegal =
    	tot_not_illegal / (tot_illegal + tot_not_illegal)
  ) %>%
	arrange(desc(prop_illegal)) %>% 
  knitr::kable()
```

##### What is the average time needed to close a request pertaining to something potentially illegal?
```{r, echo=FALSE, warning=FALSE}
# This needs mroe thinking through, as there is bound to be extraneous data here.
data_temp <-
	data_calls %>%
	filter(fix_min > 525600) %>% 
	count()

print(paste0(data_temp, " calls took more than a year to fix and were thus filtered out here."))

data_calls %>% 
	filter(status == "closed", fix_min < 525600) %>%
	group_by(illegal) %>% 
	summarise(
		avg_minutes_to_close = mean(fix_min, na.rm = TRUE),
		avg_hours_to_close = avg_minutes_to_close / 60,
		avg_days_to_close = avg_hours_to_close / 24
	) %>% 
	knitr::kable()
```

##### What is the average time needed to close a request by topic?
```{r, echo=FALSE, warning=FALSE}
data_calls %>% 
	filter(status == "closed", fix_min < 525600) %>%
	group_by(topic) %>% 
	filter(illegal != "maybe") %>% 
	summarise(
		total_num = n(),
		avg_minutes_to_close = mean(fix_min, na.rm = TRUE),
		avg_hours_to_close = avg_minutes_to_close / 60,
		avg_days_to_close = avg_hours_to_close / 24
	) %>% 
	arrange(avg_days_to_close) %>% 
	knitr::kable()
```
\newpage
### Geographic Analysis

```{r, include=FALSE}
# Prep Summary Data
data_summary <-
	data_calls %>% 
	group_by(geoid, topic) %>% 
	summarize(
		num_topic = n(),
		human = sum(req_aim == "human", na.rm = TRUE),
		non_human = sum(req_aim == "non-human", na.rm = TRUE),
		illegal = sum(illegal == "yes", na.rm = TRUE),
		not_illegal = sum(illegal == "no", na.rm = TRUE),
		adversarial = sum(adv == "yes", na.rm = TRUE),
		not_adversarial = sum(adv == "no", na.rm = TRUE)
	) %>% 
	mutate(
		total_reqs = sum(num_topic, na.rm = TRUE),
		prop_human = sum(human, na.rm = TRUE)/total_reqs,
		prop_nonhuman = sum(non_human, na.rm = TRUE)/total_reqs,
		prop_illegal = sum(illegal, na.rm = TRUE)/total_reqs,
		prop_legal = sum(not_illegal, na.rm = TRUE)/total_reqs,
		prop_adv = sum(adversarial, na.rm = TRUE)/total_reqs,
		prop_not_adv = sum(not_adversarial, na.rm = TRUE)/total_reqs
	) %>% 
	group_by(topic) %>% 
	mutate(prop_topic = num_topic/total_reqs) %>% 
	select(-num_topic, -human, -non_human, -illegal, -not_illegal, -adversarial, -not_adversarial) %>% 
	ungroup() %>% 
	spread(topic, prop_topic) %>% 
	# Join data with census metrics
	left_join(data_descriptive, by = "geoid") %>% 
	mutate(
		avg_num_reqs = total_reqs/pop_tot,
		college_educated = ed_grad + ed_bs + ed_as
	)
```

#### Volume of  Calls
#### =>Relationship Between Race and Volume of Calls
```{r, echo=FALSE, warning=FALSE}
data_summary %>% 
	filter(avg_num_reqs <= find_outlier(avg_num_reqs)) %>% 
	ggplot(aes(x = pop_wht, y = avg_num_reqs)) +
	geom_point(alpha = .08) +
	geom_boxplot(aes(group = cut_width(pop_wht, .1)), alpha = .2) +
	geom_smooth(method = "loess", se = FALSE, color = "maroon") +
	scale_y_continuous(
		breaks = get_breaks(avg_num_reqs),
    labels = scales::number_format(accuracy = .01)
  ) +
  scale_x_continuous(
  	breaks = seq(0, 1, .1),
    labels = scales::percent_format(accuracy = 1)
  ) +
	theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(color = "gray95"),
    plot.caption = element_text(hjust = 0)
  ) +
	labs(
		title = paste0("White Population vs. Avg. Volume of 311 Requests in ", data_city),
		x = "Proportion of the Population that is\nWhite Alone (Non-Hispanic)",
		y = "Number of 311 Requests per Person",
		caption = "Note: Be wary of drawing comparisons to other cities as the data may come from different time periods.\nDensity of background points indicate sample size."
	)
```

```{r, echo=FALSE, warning=FALSE}
data_summary %>% 
	filter(
		avg_num_reqs <= find_outlier(avg_num_reqs),
		pop_blk <= find_outlier("pop_blk")
	) %>% 
	ggplot(aes(x = pop_blk, y = avg_num_reqs)) +
	geom_point(alpha = .08) +
	geom_boxplot(aes(group = cut_width(pop_blk, .1)), alpha = .2) +
	geom_smooth(method = "loess", se = FALSE, color = "maroon") +
	scale_y_continuous(
		breaks = get_breaks(avg_num_reqs),
    labels = scales::number_format(accuracy = .01)
  ) +
  scale_x_continuous(
  	breaks = seq(0, 1, .1),
    labels = scales::percent_format(accuracy = 1)
  ) +
	theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(color = "gray95"),
    plot.caption = element_text(hjust = 0)
  ) +
	labs(
		title = paste0("African American Population vs. Avg. Volume of 311 Requests in ", data_city),
		x = "Proportion of the Population that is\nAfrican American Alone (Non-Hispanic)",
		y = "Number of 311 Requests per Person",
		caption = "Note: Be wary of drawing comparisons to other cities as the data may come from different time periods.\nDensity of background points indicate sample size."
	)
```

```{r, echo=FALSE, warning=FALSE}
data_summary %>% 
	filter(avg_num_reqs <= find_outlier(avg_num_reqs)) %>%
	select(
		avg_num_reqs, 
		"White" = pop_wht, 
		"African American" = pop_blk, 
		"Hispanic" = pop_his,
		"Asian" = pop_asi
	) %>% 
	gather(key = "race", value = "prop", -avg_num_reqs) %>% 
	ggplot(aes(x = prop, y = avg_num_reqs)) +
	geom_point(alpha = .04) +
	geom_boxplot(aes(group = cut_width(prop, .1)), alpha = .2) +
	geom_smooth(aes(color = race), method = "loess", se = FALSE) +
	scale_y_continuous(
		breaks = get_breaks(avg_num_reqs),
    labels = scales::number_format(accuracy = .01)
  ) +
  scale_x_continuous(
  	breaks = seq(0, 1, .1),
    labels = scales::percent_format(accuracy = 1)
  ) +
	scale_color_manual(
    values = race_colors
  ) +
	theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(color = "gray95"),
    plot.caption = element_text(hjust = 0)
  ) +
	labs(
		title = paste0("Racial Makeup vs. Avg. Volume of 311 Requests in ", data_city),
		x = "Proportion of the Population that is a Given Race",
		y = "Number of 311 Requests per Person",
		caption = "Note: Be wary of drawing comparisons to other cities as the data may come from different time periods.\nDensity of background points indicate sample size.",
		color = "Race/Ethinicity"
	)
```

\newpage
#### =>Relationship Between Home Value/Rent and Volume of Calls
```{r, echo=FALSE, warning=FALSE}
data_summary %>% 
	filter(
		avg_num_reqs <= find_outlier(avg_num_reqs), 
		med_val <= find_outlier(med_val)
	) %>%
	ggplot(aes(x = med_val, y = avg_num_reqs)) +
	geom_point(alpha = .08) +
	geom_boxplot(
		aes(group = cut_width(med_val, get_break_width("med_val"))),
		alpha = .2
	) +
	geom_smooth(method = "loess", se = FALSE, color = "maroon") +
	scale_y_continuous(
		breaks = get_breaks(avg_num_reqs),
    labels = scales::number_format(accuracy = .01)
  ) +
  scale_x_continuous(
  	breaks = get_breaks(med_val),
    labels = scales::comma_format(accuracy = 1000, prefix = "$")
  ) +
	theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(color = "gray95"),
    plot.caption = element_text(hjust = 0)
  ) +
	labs(
		title = paste0("Median Home Value vs. Avg. Volume of 311 Requests in ", data_city),
		x = "Median Home Value ($)",
		y = "Number of 311 Requests per Person",
		caption = "Note: Be wary of drawing comparisons to other cities as the data may come from different time periods.\nDensity of background points indicate sample size."
	)
```

```{r, echo=FALSE, warning=FALSE}
data_summary %>% 
	filter(
		avg_num_reqs <= find_outlier(avg_num_reqs), 
		med_ren <= find_outlier(med_ren)
	) %>%
	ggplot(aes(x = med_ren, y = avg_num_reqs)) +
	geom_point(alpha = .08) +
	geom_boxplot(
		aes(group = cut_width(med_ren, get_break_width("med_ren"))),
		alpha = .2
	) +
	geom_smooth(method = "loess", se = FALSE, color = "maroon") +
	scale_y_continuous(
		breaks = get_breaks(avg_num_reqs),
    labels = scales::number_format(accuracy = .01)
  ) +
  scale_x_continuous(
  	breaks = get_breaks(med_ren),
    labels = scales::comma_format(accuracy = 100, prefix = "$")
  ) +
	theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(color = "gray95"),
    plot.caption = element_text(hjust = 0)
  ) +
	labs(
		title = paste0("Median Rent vs. Avg. Volume of 311 Requests in ", data_city),
		x = "Median Rent ($)",
		y = "Number of 311 Requests per Person",
		caption = "Note: Be wary of drawing comparisons to other cities as the data may come from different time periods.\nDensity of background points indicate sample size."
	)
```

\newpage
#### =>Relationship Between Education and Volume of Calls
```{r, echo=FALSE, warning=FALSE}
data_summary %>% 
	filter(
		avg_num_reqs <= find_outlier(avg_num_reqs)
	) %>%
	ggplot(aes(x = college_educated, y = avg_num_reqs)) +
	geom_point(alpha = .08) +
	geom_boxplot(
		aes(group = cut_width(college_educated, .1)),
		alpha = .2
	) +
	geom_smooth(method = "loess", se = FALSE, color = "maroon") +
	scale_y_continuous(
		breaks = get_breaks(avg_num_reqs),
    labels = scales::number_format(accuracy = .01)
  ) +
  scale_x_continuous(
  	breaks = seq(0, 1, .1),
    labels = scales::percent_format(accuracy = 1)
  ) +
	theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(color = "gray95"),
    plot.caption = element_text(hjust = 0)
  ) +
	labs(
		title = paste0("Proportion College Educated vs. Avg. Volume of 311 Requests in ", data_city),
		x = "Proportion College Educated",
		y = "Number of 311 Requests per Person",
		caption = "Note: Be wary of drawing comparisons to other cities as the data may come from different time periods.\nDensity of background points indicate sample size."
	)
```

\newpage
#### =>Relationship Between Employment and Volume of Calls
```{r, echo=FALSE, warning=FALSE}
data_summary %>% 
	filter(
		avg_num_reqs <= find_outlier(avg_num_reqs),
		emp_une <= find_outlier(emp_une)
	) %>%
	ggplot(aes(x = emp_une, y = avg_num_reqs)) +
	geom_point(alpha = .08) +
	geom_boxplot(
		aes(group = cut_width(emp_une, .05)),
		alpha = 0
	) +
	geom_smooth(method = "loess", se = FALSE, color = "maroon") +
	scale_y_continuous(
		breaks = get_breaks(avg_num_reqs),
    labels = scales::number_format(accuracy = .01)
  ) +
  scale_x_continuous(
  	breaks = seq(0, 1, .05),
    labels = scales::percent_format(accuracy = 1)
  ) +
	theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(color = "gray95"),
    plot.caption = element_text(hjust = 0)
  ) +
	labs(
		title = paste0("Unemployment Rate vs. Avg. Volume of 311 Requests in ", data_city),
		x = "Unemployment Rate",
		y = "Number of 311 Requests per Person",
		caption = "Note: Be wary of drawing comparisons to other cities as the data may come from different time periods.\nDensity of background points indicate sample size."
	)
```

\newpage
#### Adversarial Calls
#### =>Relationship Between Race and Adversarial Calls
```{r, echo=FALSE, warning=FALSE}
data_summary %>% 
	filter(prop_adv <= find_outlier(prop_adv)) %>% 
	ggplot(aes(x = pop_wht, y = prop_adv)) +
	geom_point(alpha = .08) +
	geom_boxplot(aes(group = cut_width(pop_wht, .1)), alpha = .2) +
	geom_smooth(method = "loess", se = FALSE, color = "maroon") +
	scale_y_continuous(
		breaks = get_breaks(prop_adv),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_x_continuous(
  	breaks = seq(0, 1, .1),
    labels = scales::percent_format(accuracy = 1)
  ) +
	theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(color = "gray95"),
    plot.caption = element_text(hjust = 0)
  ) +
	labs(
		title = paste0("White Population vs. Proportion of Adversarial 311 Requests in ", data_city),
		x = "Proportion of the Population that is\nWhite Alone (Non-Hispanic)",
		y = "Proportion of 311 Requests\nDesignated Adversarial",
		caption = "Note: Be wary of drawing comparisons to other cities as the data may come from different time periods.\nDensity of background points indicate sample size."
	)
```

```{r, echo=FALSE, warning=FALSE}
data_summary %>% 
	filter(prop_adv <= find_outlier(prop_adv)) %>% 
	ggplot(aes(x = pop_nw, y = prop_adv)) +
	geom_point(alpha = .08) +
	geom_boxplot(aes(group = cut_width(pop_nw, .1)), alpha = .2) +
	geom_smooth(method = "loess", se = FALSE, color = "maroon") +
	scale_y_continuous(
		breaks = get_breaks(prop_adv),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_x_continuous(
  	breaks = seq(0, 1, .1),
    labels = scales::percent_format(accuracy = 1)
  ) +
	theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(color = "gray95"),
    plot.caption = element_text(hjust = 0)
  ) +
	labs(
		title = paste0("Non-White Population vs. Proportion of Adversarial 311 Requests in ", data_city),
		x = "Proportion of the Population that is\nNon-White Alone",
		y = "Proportion of 311 Requests\nDesignated Adversarial",
		caption = "Note: Be wary of drawing comparisons to other cities as the data may come from different time periods.\nDensity of background points indicate sample size."
	)
```

```{r, echo=FALSE, warning=FALSE}
data_summary %>% 
	filter(
		prop_adv <= find_outlier(prop_adv),
		pop_blk <= find_outlier(pop_blk)
	) %>% 
	ggplot(aes(x = pop_blk, y = prop_adv)) +
	geom_point(alpha = .08) +
	geom_boxplot(aes(group = cut_width(pop_blk, .1)), alpha = .2) +
	geom_smooth(method = "loess", se = FALSE, color = "maroon") +
	scale_y_continuous(
		breaks = get_breaks(prop_adv),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_x_continuous(
  	breaks = seq(0, 1, .1),
    labels = scales::percent_format(accuracy = 1)
  ) +
	theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(color = "gray95"),
    plot.caption = element_text(hjust = 0)
  ) +
	labs(
		title = paste0("African American Population vs. Proportion of Adversarial 311 Requests\nin ", data_city),
		x = "Proportion of the Population that is\nAfrican American Alone (Non-Hispanic)",
		y = "Proportion of 311 Requests\nDesignated Adversarial",
		caption = "Note: Be wary of drawing comparisons to other cities as the data may come from different time periods.\nDensity of background points indicate sample size."
	)
```

```{r, echo=FALSE, warning=FALSE}
data_summary %>% 
	filter(prop_adv <= find_outlier(prop_adv)) %>% 
	select(
		prop_adv, 
		"White" = pop_wht, 
		"African American" = pop_blk, 
		"Hispanic" = pop_his,
		"Asian" = pop_asi
	) %>% 
	gather(key = "race", value = "prop", -prop_adv) %>% 
	ggplot(aes(x = prop, y = prop_adv)) +
	geom_point(alpha = .08) +
	geom_boxplot(aes(group = cut_width(prop, .1)), alpha = .2) +
	geom_smooth(method = "loess", se = FALSE) +
	scale_y_continuous(
		breaks = get_breaks(prop_adv),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_x_continuous(
  	breaks = seq(0, 1, .1),
    labels = scales::percent_format(accuracy = 1)
  ) +
	facet_wrap(~race, scales = "free_x") +
	theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(color = "gray95"),
    plot.caption = element_text(hjust = 0)
  ) +
	labs(
		title = paste0("Racial/Ethnic Population vs. Proportion of Adversarial 311 Requests\nin ", data_city),
		x = "Proportion of the Population that is\nA Given Race/Ethnicity",
		y = "Proportion of 311 Requests\nDesignated Adversarial",
		caption = "Note: Be wary of drawing comparisons to other cities as the data may come from different time periods.\nDensity of background points indicate sample size."
	)
```

\newpage
#### =>Relationship Between Home Value/Rent and Adversarial Calls
```{r, echo=FALSE, warning=FALSE}
data_summary %>% 
	filter(
		prop_adv <= find_outlier(prop_adv), 
		med_val <= find_outlier(med_val)
	) %>%
	ggplot(aes(x = med_val, y = prop_adv)) +
	geom_point(alpha = .08) +
	geom_boxplot(
		aes(group = cut_width(med_val, get_break_width("med_val"))),
		alpha = .2
	) +
	geom_smooth(method = "loess", se = FALSE, color = "maroon") +
	scale_y_continuous(
		breaks = get_breaks(prop_adv),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_x_continuous(
  	breaks = get_breaks(med_val),
    labels = scales::comma_format(accuracy = 1000, prefix = "$")
  ) +
	theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(color = "gray95"),
    plot.caption = element_text(hjust = 0)
  ) +
	labs(
		title = paste0("Median Home Value vs. Proportion of Adversarial 311 Requests in\n", data_city),
		x = "Median Home Value ($)",
		y = "Proportion of 311 Requests\nDesignated Adversarial",
		caption = "Note: Be wary of drawing comparisons to other cities as the data may come from different time periods.\nDensity of background points indicate sample size."
	)
```

```{r, echo=FALSE, warning=FALSE}
data_summary %>% 
	filter(
		prop_adv <= find_outlier(prop_adv), 
		med_ren <= find_outlier(med_ren)
	) %>%
	ggplot(aes(x = med_ren, y = prop_adv)) +
	geom_point(alpha = .08) +
	geom_boxplot(
		aes(group = cut_width(med_ren, get_break_width("med_ren"))),
		alpha = .2
	) +
	geom_smooth(method = "loess", se = FALSE, color = "maroon") +
	scale_y_continuous(
		breaks = get_breaks(prop_adv),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_x_continuous(
  	breaks = get_breaks(med_ren),
    labels = scales::comma_format(accuracy = 100, prefix = "$")
  ) +
	theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(color = "gray95"),
    plot.caption = element_text(hjust = 0)
  ) +
	labs(
		title = paste0("Median Rent vs. Proportion of Adversarial 311 Requests in\n", data_city),
		x = "Median Rent ($)",
		y = "Proportion of 311 Requests\nDesignated Adversarial",
		caption = "Note: Be wary of drawing comparisons to other cities as the data may come from different time periods.\nDensity of background points indicate sample size."
	)
```

\newpage
#### =>Relationship Between Education and Adversarial Calls
```{r, echo=FALSE, warning=FALSE}
data_summary %>% 
	mutate(college_educated = ed_grad + ed_bs + ed_as) %>% 
	filter(
		prop_adv <= find_outlier(prop_adv)
	) %>%
	ggplot(aes(x = college_educated, y = prop_adv)) +
	geom_point(alpha = .08) +
	geom_boxplot(
		aes(group = cut_width(college_educated, .1)),
		alpha = .2
	) +
	geom_smooth(method = "loess", se = FALSE, color = "maroon") +
	scale_y_continuous(
		breaks = get_breaks(prop_adv),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_x_continuous(
  	breaks = seq(0, 1, .1),
    labels = scales::percent_format(accuracy = 1)
  ) +
	theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(color = "gray95"),
    plot.caption = element_text(hjust = 0)
  ) +
	labs(
		title = paste0("Proportion College Educated vs. Proportion of Adversarial\n 311 Requests in ", data_city),
		x = "Proportion College Educated",
		y = "Proportion of 311 Requests\nDesignated Adversarial",
		caption = "Note: Be wary of drawing comparisons to other cities as the data may come from different time periods.\nDensity of background points indicate sample size."
	)
```

\newpage
#### =>Relationship Between Employment and Adversarial Calls
```{r, echo=FALSE, warning=FALSE}
data_summary %>% 
	filter(
		prop_adv <= find_outlier(prop_adv),
		emp_une <= find_outlier(emp_une)
	) %>%
	ggplot(aes(x = emp_une, y = prop_adv)) +
	geom_point(alpha = .08) +
	geom_boxplot(
		aes(group = cut_width(emp_une, .05)),
		alpha = 0
	) +
	geom_smooth(method = "loess", se = FALSE, color = "maroon") +
	scale_y_continuous(
		breaks = get_breaks(prop_adv),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_x_continuous(
  	breaks = seq(0, 1, .05),
    labels = scales::percent_format(accuracy = 1)
  ) +
	theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(color = "gray95"),
    plot.caption = element_text(hjust = 0)
  ) +
	labs(
		title = paste0("Unemployment Rate vs. Proportion of Adversarial\n 311 Requests in ", data_city),
		x = "Unemployment Rate",
		y = "Proportion of 311 Requests\nDesignated Adversarial",
		caption = "Note: Be wary of drawing comparisons to other cities as the data may come from different time periods.\nDensity of background points indicate sample size."
	)
```

\newpage
### Mapping
```{r, include=FALSE}
# Filters out tracts that are not really part of the areas we are looking at
data_summary <-
	data_summary %>% 
	filter(!(geoid %in% c("06041131100", "06075017902", "25017341902", "25025990101")))
```

#### Mapping Demographics
#### =>Population Density
```{r, echo=FALSE, warning=FALSE, message=FALSE}
make_map(
	metric = pop_tot,
	metric_type = "number", 
	map_title = paste0("Total Population in ", get_full_city_name()), 
	legend_title = "Total Population in A Given Census Tract"
)
```

\newpage
#### =>Mapping Number of Calls
```{r, echo=FALSE, warning=FALSE, message=FALSE}
map_calls <-
	make_map(
		metric = avg_num_reqs,
		metric_type = "number", 
		map_title = paste0("Average Number of Requests\nper Person in ", get_full_city_name()), 
		legend_title = "Average Number of Request per Person"
	)

map_calls
```

\newpage
#### =>Mapping Race
```{r, echo=FALSE, warning=FALSE, message=FALSE}
map_white <-
	make_map(
		metric = pop_wht,
		metric_type = "percent", 
		map_title = paste0("Proportion of the Population\nWhite Alone (Non-Hispanic) in ", get_full_city_name()), 
		legend_title = "% of Population"
	)

map_white
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
map_nw <-
	make_map(
		metric = pop_nw,
		metric_type = "percent", 
		map_title = paste0("Proportion of the Population\n Non-White in ", get_full_city_name()), 
		legend_title = "% of Population"
	)

map_nw
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
map_his <-
	make_map(
		metric = pop_his,
		metric_type = "percent", 
		map_title = paste0("Proportion of the Population\n Hispanic in ", get_full_city_name()), 
		legend_title = "% of Population"
	)

map_his
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
map_aa <- 
	make_map(
		metric = pop_blk,
		metric_type = "percent", 
		map_title = 
			paste0("Proportion of the Population\nAfrican American in ", get_full_city_name()), 
		legend_title = "% of Population"
	)

map_aa
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
map_asian <-
	make_map(
		metric = pop_asi,
		metric_type = "percent", 
		map_title = paste0("Proportion of the Population\nAsian in ", get_full_city_name()), 
		legend_title = "% of Population"
	)

map_asian
```

\newpage
#### =>Mapping Rent
```{r, echo=FALSE, warning=FALSE, message=FALSE}
map_rent <- 
	make_map(
		metric = med_ren,
		rev_scale = "higher is better",
		metric_type = "rent", 
		map_title = paste0("Median Rent in ", get_full_city_name()), 
		legend_title = "Median Rent ($)"
	)

map_rent
```

\newpage
#### =>Mapping Education
```{r, echo=FALSE, warning=FALSE, message=FALSE}
map_ed <- 
	make_map(
		metric = college_educated,
		rev_scale = "higher is better",
		metric_type = "percent", 
		map_title = paste0("% of Population College Educated\nin ", get_full_city_name()), 
		legend_title = "% of Population College Educated"
	)

map_ed
```

\newpage
#### =>Mapping Income
```{r, echo=FALSE, warning=FALSE, message=FALSE}
map_income <- 
	make_map(
		metric = med_inc,
		rev_scale = "higher is better",
		metric_type = "value", 
		map_title = paste0("Median Income in ", get_full_city_name()), 
		legend_title = "Median Income ($)"
	)

map_income
```

\newpage
#### Mapping 311 Requests
#### =>Mapping Adversarial Requests
```{r, echo=FALSE, warning=FALSE, message=FALSE}
map_adv <- 
	make_map(
		metric = prop_adv,
		metric_type = "percent", 
		map_title = paste0("% Adversarial 311 Requests in\n", get_full_city_name()), 
		legend_title = "% of 311 Request Designated Adversarial"
	)

map_adv
```

\newpage
#### =>Mapping Requests Regarding Potentially Illegal Activities
```{r, echo=FALSE, warning=FALSE, message=FALSE}
map_ill <- 
	make_map(
		metric = prop_illegal,
		metric_type = "percent", 
		map_title = 
			paste0("% 311 Requests Pertaining to Potentially\nIllegal Activities in ", get_full_city_name()), 
		legend_title = "% of 311 Requests Regarding Potentially Illegal Activity"
	)

map_ill
```

\newpage
#### =>Mapping Requests Regarding Housing and Homeless Issues
```{r, echo=FALSE, warning=FALSE, message=FALSE}
if (data_city != "BOS") {
	map_house <- 
		make_map(
			metric = housing,
			metric_type = "percent", 
			map_title = 
				paste0("% 311 Requests Regarding\nHousing/Homeless Issues in ", get_full_city_name()), 
			legend_title = "% of 311 Requests"
		)

	map_house
}
```

\newpage
#### =>Mapping Requests Regarding Abandoned Property
```{r, echo=FALSE, warning=FALSE, message=FALSE}
map_abandoned <- 
	make_map(
		metric = `abandoned bike/vehicle`,
		metric_type = "percent", 
		map_title = 
			paste0("% 311 Requests Regarding Abandoned\nBikes/Vehicles in ", get_full_city_name()), 
		legend_title = "% of 311 Requests"
	)

map_abandoned
```

\newpage
#### =>Mapping Requests Regarding Graffiti
```{r, echo=FALSE, warning=FALSE, message=FALSE}
map_graffiti <- 
	make_map(
		metric = graffiti,
		metric_type = "percent", 
		map_title = 
			paste0("% 311 Requests Regarding Graffiti\nin ", get_full_city_name()), 
		legend_title = "% of 311 Requests"
	)

map_graffiti
```

\newpage
#### =>Mapping Requests Regarding Noise
```{r, echo=FALSE, warning=FALSE, message=FALSE}
map_noise <- 
	make_map(
		metric = noise,
		metric_type = "percent", 
		map_title = 
			paste0("% 311 Requests Regarding Noise\nin ", get_full_city_name()), 
		legend_title = "% of 311 Requests"
	)

map_noise
```

\newpage
#### High Level View
#### => Mapping Racial Diversity
```{r, echo=FALSE, warning=FALSE, fig.width=15, fig.height=10, message=FALSE}
map_calls + map_white + map_aa + map_his + plot_layout()
```

\newpage
#### =>Mapping Demographic Composition
```{r, echo=FALSE, warning=FALSE, fig.width=15, fig.height=10, message=FALSE}
map_white + map_income + map_ed + map_rent + plot_layout()
```

\newpage
#### => Mapping Composition of Adversarial Requests
```{r, echo=FALSE, warning=FALSE, fig.width=15, fig.height=10, message=FALSE}
if (data_city != "BOS") {
	map_graffiti + map_noise + map_house + map_abandoned + plot_layout()
} else {
	map_graffiti + map_noise + map_abandoned + plot_layout(ncol = 2)
}
```
