---
title: "mse231_a0"
author: "Michael Spencer"
date: "9/25/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Will eventually want to run a simulation 10,000 times. Given simulation should 
simulate the roll of a dice, in which rolls resulting in odds are thrown out. 
Will stop when a 6 is rolled, and store that roll in a summed variable. 
Small simulation will give a single dice roll count. Larger simulation will 
sum these counts and divide by n.

```{r}
n_sim <- 1e5
norm_dice <- c(1, 2, 3, 4, 5, 6)
total_rolls <- 0
```

Find Conditioned Dice Function
```{r}
find_conditioned_dice <- function() {
  
  whole_roll = integer()
  trip = FALSE
  
  while (!trip) {
    
    roll <- sample(norm_dice, 1, replace = TRUE)
    
    if (roll %in% c(1, 3, 5)) {
      whole_roll = integer()
    } else {
      whole_roll = c(whole_roll, roll)
    }  
    
    if (roll == 6) trip = TRUE
  }
  
  whole_roll
  
}
```

# Roll Function
```{r}
roll_dice <- function() {
  
  dice <- find_conditioned_dice()
  
  if (length(dice) == 1) {
    roll_count = 1
  } else {
    roll_count <- 0
    result <- 0
  
    while (result != 6) {
    
      result <- sample(dice, 1, replace = TRUE)
      
      roll_count <- roll_count + 1
    
    }
  }
  
  roll_count
}
```

# Simulation
```{r}
for (i in 1:n_sim) {
  
  total_rolls <- total_rolls + roll_dice()
  
}

total_rolls / n_sim
```

```{r}
find_conditioned_dice_2 <- function() {
  
  whole_roll = integer()
  trip = FALSE
  
  while (!trip) {
    
    roll <- sample(norm_dice, 1, replace = TRUE)
    
    if (roll %in% c(1, 3, 5)) {
      whole_roll = integer()
    } else {
      whole_roll = c(whole_roll, roll)
    }  
    
    if (roll == 6) trip = TRUE
  }
  
  length(whole_roll)
  
}
```

```{r}
for (i in 1:n_sim) {
  
  total_rolls <- total_rolls + find_conditioned_dice_2()
  
}

total_rolls / n_sim
```

