---
title: "311 Exploratory Analysis"
author: "Michael Spencer, "
date: "11/21/2019"
output: pdf_document
params:
  city: "SFO"
  write: "no"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

### Pathways
```{r}
project_dir <- here::here()
data_city <- params$city
data_name <- paste0(data_city, "_data_census")
```

### Parameters
```{r}
write_my_files <- params$write # If you'd like to write out a .shp and .tsv file, use "yes", otherwise "no".
```

### Sourcing and Libraries
```{r, include=FALSE}
### Libraries
if (!require(sf)) install.packages("sf")
library(sf)

if (!require(tidyverse)) install.packages("tidyverse")
library(tidyverse)

if (!require(lubridate)) install.packages("lubridate")
library(lubridate)

if (!require(googlesheets4)) install.packages("googlesheets4")
library(googlesheets4)

### Source prep and cleaning files to load data
source(paste0(project_dir, "/scripts/311/final_clean.R"))
```

## Checks
```{r, echo=FALSE}
# Check for uncategorized service requests and notify user
data_temp <- 
	data_calls %>% 
	filter(is.na(topic)) %>% 
	distinct(srvc_nm)

if (nrow(data_temp) > 0) {
	print(paste0(
		"There are currently ", 
		nrow(data_temp), 
		" uncategorized services in ", 
		data_city, 
		". See them below:"))
	
	for (i in data_temp) {
		print(i)
	}
} else {
	print("All services in the data have been classified!")
}
```

Potential duplicates. These are only adressed if it is believed they would present a significant issue in analysis.
```{r}
# Check for apparent duplicates and address if there is a problem
data_calls %>% 
	group_by(address, req_dt, updt_dt, topic) %>% 
	count(sort = TRUE) %>% 
	filter(n > 1) %>% 
	knitr::kable()
```


## Analysis

### Base Benchmark Analysis (Non-Geographic)

##### What is the distribution of call by topic?
```{r, echo=FALSE}
data_calls %>%
  count(topic, sort = TRUE) %>%
  mutate(prop_total = (n / sum(n)) %>% round(digits = 3)) %>%
  knitr::kable()

data_calls %>%
  count(topic, sort = TRUE) %>%
  mutate(
    prop = n / sum(n, na.rm = TRUE),
    topic = topic %>% fct_inorder() %>% fct_rev()
  ) %>%
  head(10) %>%
  ggplot(aes(x = topic, y = prop)) +
  geom_point() +
  coord_flip() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    title = "Most Frequent Request Topics",
    x = "Request Topic",
    y = "Proportion of Total Requests"
  )
```

##### Within each topic, what are the most frequent services requested?
```{r, include=FALSE}
data_temp <-
  data_calls %>%
  group_by(topic, srvc_nm) %>%
  summarize(total_service = n()) %>%
  mutate(
    total_topic = sum(total_service, na.rm = TRUE),
    service_prop_topic = (total_service / total_topic) %>% round(digits = 3)
  ) %>%
  ungroup() %>%
  mutate(topic_prop_all = total_topic / sum(total_service, na.rm = TRUE) %>% round(digits = 3)) %>%
  arrange(desc(total_topic), desc(total_service))

data_temp
```

```{r, echo=FALSE}
list_topics <- data_temp %>%
  distinct(topic) %>%
  pull(topic)

plot_top_services <- function(tp) {
  data_temp %>%
    filter(topic == tp) %>%
    head(3) %>%
    mutate(srvc_nm = srvc_nm %>% fct_inorder() %>% fct_rev()) %>%
    ggplot(aes(x = srvc_nm, y = service_prop_topic)) +
    geom_point() +
    coord_flip() +
    scale_y_continuous(labels = scales::percent_format()) +
    labs(
      title = paste0("Frequently Requested Services: ", tp %>% str_to_title()),
      x = "Requested Service",
      y = paste0("Proportion of Total Requests in Topic")
    )
}

map(list_topics, plot_top_services)
```

##### What is the proportion of requests that may be adversarial by topic?
```{r, echo=FALSE}
# Excludes "maybe" adversarial in calculations.

data_calls %>%
  group_by(topic) %>%
  summarise(
    tot_adversarial = sum(adv == "yes", na.rm = TRUE),
    tot_not_adversarial = sum(adv == "no", na.rm = TRUE)
  ) %>%
  mutate(
    prop_adversarial =
      tot_adversarial / (tot_adversarial + tot_not_adversarial),
    prop_not_adversarial =
    	tot_not_adversarial / (tot_adversarial + tot_not_adversarial)
  ) %>%
	arrange(desc(prop_adversarial)) %>% 
  knitr::kable()
```

##### What is the proportion of requests that may involve illegal acitivity by topic?
```{r, echo=FALSE}
# Excludes "maybe" illegal in calculations.

data_calls %>%
  group_by(topic) %>%
  summarise(
    tot_illegal = sum(illegal == "yes", na.rm = TRUE),
    tot_not_illegal = sum(illegal == "no", na.rm = TRUE)
  ) %>%
  mutate(
    prop_illegal =
      tot_illegal / (tot_illegal + tot_not_illegal),
    prop_not_illegal =
    	tot_not_illegal / (tot_illegal + tot_not_illegal)
  ) %>%
	arrange(desc(prop_illegal)) %>% 
  knitr::kable()
```

##### What is the average time needed to close a request pertaining to something potentially illegal?
```{r}
# This needs mroe thinking through, as there is bound to be extraneous data here.

# data_calls %>% 
# 	summary()
# 
# data_calls %>% 
# 	mutate()

data_calls %>% 
	filter(status == "closed", fix_min < 300000) %>%
	group_by(illegal) %>% 
	summarise(
		avg_minutes_to_close = mean(fix_min, na.rm = TRUE),
		avg_hours_to_close = avg_minutes_to_close / 60,
		avg_days_to_close = avg_hours_to_close / 24
	)
```


##### What is the average time needed to close a request by topic?

### Geographic Analysis
